### 2020-02-24 RFCs/HDF5/VOL/user_guide/body.tex
Updated VOL user guide and connector author guide to be in agreement with final 1.12.0 changes.
Former-commit-id: f656be3383755816b47e431b1dabfeb7ee3e402a

Exactly how you go about setting a VOL connector in a fapl, will depend on the complexity of the VOL connector and how much control you have over the application's source code.

@@

\quad\quad {\tt hid\_t H5VLregister\_connector(const H5VL\_class\_t *cls, hid\_t vipl\_id)}

\quad\quad {\tt hid\_t H5VLregister\_connector\_by\_name(const char *connector\_name, hid\_t vipl\_id)}

\quad\quad {\tt hid\_t H5VLregister\_connector\_by\_value(H5VL\_class\_value\_t connector\_value, hid\_t vipl\_id)}

When used with a plugin, these functions will check to see if an appropriate plugin with a matching name, value, etc. is already loaded and check the plugin path (see above) for matching plugins if this is not true. The functions return {\tt H5I\_INVALID\_HID} if they are unable to register the connector. Most people will use the {\tt \_by\_name()} or {\tt \_by\_value} versions of this API call. The call that takes an {\tt H5VL\_class\_t} struct is considered a lower-level call this is more commonly used by connector authors in connector-specific setup/registration code. Many VOL connectors will provide a connector-specific init call that will load and register the connector for you.

@@

\thgfuturewarning

@@

\quad\quad {\tt herr\_t H5Pset\_vol(hid\_t plist\_id, hid\_t vol\_id, vol\_info)}

It takes the ID of the file access property list, the ID of the registered VOL connector, and a pointer to whatever connector-specific data the connector is expecting. This will usually be a data struct specified in the connector's header.

@@

\quad\quad {\tt herr\_t H5VLconnector\_str\_to\_info(const char *str, hid\_t connector\_id, void **info)}

@@

\quad\quad {\tt herr\_t H5VLfree\_connector\_info(hid\_t connector\_id, void *vol\_info)}

@@

@@

The VOL was engineered to be as unobtrusive as possible and, when a connector which implements most/all of the data model functionality is in use, most applications should require little, if any, modification. As mentioned in the quick start section, most modifications will probably consist of connector setup code (which can usually be accomplished via the environment variable) and protecting native file format functions.

\subsection{Specific API Call Substitutions}
\subsubsection{${\tt H5Fis\_hdf5()} \rightarrow {\tt H5Fis\_accessible()}$}

@@

\subsubsection{${\tt H5Oget\_info[1|2]()} \rightarrow {\tt H5Oget\_info3()} {\tt H5Oget\_native\_info()}$}

\thgfuturewarning

The {\tt H5Oget\_info1()} and {\tt H5Oget\_info2()} family of HDF5 API calls are often used by user code to obtain information about an object in the file, however these calls return a struct which contains native information and are thus currently handled via the native connector's \textit{object optional} callback and so are not handled by most external VOL connectors.

These calls will be separated into two functions: one for getting an object's data model information ({\tt H5Oget\_info3()}, which will go through the \textit{object get} callback), and another for returning an object's native file format information ({\tt H5Oget\_native\_info()}, which will go through the native connector's \textit{object optional} callback). These API calls will use new {\tt H5O\_info2\_t} and {\tt H5O\_native\_info\_t} structs, respectively, to hold the returned data.

This feature is under development and this section will be updated when the feature is complete.

\subsubsection{Optional: ${\tt H5Ovisit[1|2]()} \rightarrow {\tt H5Ovisit3()}$}

\thgfuturewarning

The {\tt H5Ovisit()} family of API functions uses the {\tt H5O\_info\_t} struct in its callback function:

\quad \quad {\tt typedef herr\_t (*H5O\_iterate\_t)(hid\_t obj, const char *name, const H5O\_info\_t *info, void *op\_data) }

A new callback that takes the updated, data-model-only struct will replace the old callback in new {\tt H5Ovisit3} API calls. Note that replacing this function is optional as it goes through the VOL's \textit{object specific} callback.

As with the {\tt H5Oget\_info()} work, this feature is under development and this section will be updated when the feature is complete.

@@

@@

\section{Compatibility}
\subsection{Introspection / Feature Flags}
\thgfuturewarning

Some VOL connectors will not implement all the functionality available in the HDF5 library, especially in the early stages of development. Unfortunately, there is currently no easy way to determine if a VOL connector implements particular API calls or groups of calls.

We are working on an introspection mechanism, possibly involving a set of feature or capabilities flags and will have that available in a future release.

@@

\begin{longtable}{ |>{\raggedright\arraybackslash}p{\linewidth}| }
    \hline
    H5Aget\_num\_attrs (deprecated) \\
    H5Aiterate1 (deprecated) \\
    \hline
    H5Ddebug \\
    H5Dformat\_convert \\
    H5Dget\_chunk\_index\_type \\
    H5Dget\_chunk\_info \\
    H5Dget\_chunk\_info\_by\_coord \\
    H5Dget\_chunk\_storage\_size \\
    H5Dget\_num\_chunks \\
    H5Dread\_chunk H5Dwrite\_chunk \\
    \hline
    H5FD* \\
    \hline
    H5Fclear\_elink\_file\_cache \\
    H5Fformat\_convert \\
    H5Fget\_dset\_no\_attrs\_hint \\
    H5Fget\_eoa H5Fget\_file\_image \\
    H5Fget\_filesize \\
    H5Fget\_free\_sections \\
    H5Fget\_freespace \\
    H5Fget\_info1 (deprecated) \\
    H5Fget\_info2 \\
    H5Fget\_mdc\_config \\
    H5Fget\_mdc\_hit\_rate \\
    H5Fget\_mdc\_image\_info \\
    H5Fget\_mdc\_logging\_status \\
    H5Fget\_mdc\_size \\
    H5Fget\_metadata\_read\_retry\_info \\
    H5Fget\_mpi\_atomicity \\
    H5Fget\_page\_buffering\_stats \\
    H5Fget\_vfd\_handle \\
    H5Fincrement\_filesize \\
    H5Fis\_hdf5 (deprecated) \\
    H5Freset\_mdc\_hit\_rate\_stats \\
    H5Freset\_page\_buffering\_stats \\
    H5Fset\_dset\_no\_attrs\_hint \\
    H5Fset\_latest\_format (deprecated) \\
    H5Fset\_libver\_bounds \\
    H5Fset\_mdc\_config \\
    H5Fset\_mpi\_atomicity \\
    H5Fstart\_mdc\_logging \\
    H5Fstart\_swmr\_write \\
    H5Fstop\_mdc\_logging \\
    \hline
    H5Gget\_comment (deprecated) \\
    H5Giterate (deprecated) \\
    H5Gget\_info \\
    H5Gget\_info\_by\_name \\
    H5Gget\_info\_by\_idx \\
    H5Gget\_objinfo (deprecated) \\
    H5Gget\_objname\_by\_idx (deprecated) \\
    H5Gget\_objtype\_by\_idx (deprecated) \\
    H5Gset\_comment (deprecated) \\
    \hline
    H5Oare\_mdc\_flushes\_disabled \\
    H5Odisable\_mdc\_flushes \\
    H5Oenable\_mdc\_flushes \\
    H5Oget\_comment \\
    H5Oget\_comment\_by\_name \\
    H5Oget\_info\_by\_idx1 (deprecated) \\
    H5Oget\_info\_by\_idx2 \\
    H5Oget\_info\_by\_name1 (deprecated) \\
    H5Oget\_info\_by\_name2 \\
    H5Oget\_info1 (deprecated) \\
    H5Oget\_info2 \\
    H5Oset\_comment \\
    H5Oset\_comment\_by\_name \\
    \hline
\caption{Alphabetical list of HDF5 API calls specific to the native VOL connector}
\end{longtable}

>>>>

Exactly how you go about setting a VOL connector in a fapl, will depend on the complexity of the VOL connector and how much control you have over the application's source code.
Note that the environment variable method, though convenient, has some limitations in its implementation, which are discussed below.

@@

\begin{lstlisting}
  hid\_t H5VLregister\_connector\_by\_name(const char *connector\_name, hid\_t vipl\_id)

  hid\_t H5VLregister\_connector\_by\_value(H5VL\_class\_value\_t connector\_value, hid\_t vipl\_id)
\end{lstlisting}

When used with a plugin, these functions will check to see if an appropriate plugin with a matching name, value, etc. is already loaded and check the plugin path (see above) for matching plugins if this is not true. The functions return {\tt H5I\_INVALID\_HID} if they are unable to register the connector. Many VOL connectors will provide a connector-specific init call that will load and register the connector for you.

@@

@@

\begin{lstlisting}
  herr\_t H5Pset\_vol(hid\_t plist\_id, hid\_t new\_vol\_id, const void *new\_vol\_info)
\end{lstlisting}

It takes the ID of the file access property list, the ID of the registered VOL connector, and a pointer to whatever connector-specific data the connector is expecting. This will usually be a data struct specified in the connector's header or a NULL pointer if the connecter requires no special information (as in the native VOL connector).

@@

\begin{lstlisting}
  herr\_t H5VLconnector\_str\_to\_info(const char *str, hid\_t connector\_id, void **info)
\end{lstlisting}

@@

\begin{lstlisting}
  herr\_t H5VLfree\_connector\_info(hid\_t connector\_id, void *vol\_info)
\end{lstlisting}

@@

NOTE: Implementing the environment variable in this way means that setting the native VOL connector becomes somewhat awkward as there is no explicit HDF5 API call to do this. Instead you will need to get the native VOL connector's ID via {\tt H5VLget\_connector\_id\_by\_value(H5\_VOL\_NATIVE)} and set it manually in the fapl using {\tt H5Pset\_vol()}.

@@

The VOL was engineered to be as unobtrusive as possible and, when a connector which implements most/all of the data model functionality is in use, many applications will require little, if any, modification. As mentioned in the quick start section, most modifications will probably consist of connector setup code (which can usually be accomplished via the environment variable), adapting code to use the new token-based API calls, and protecting native-VOL-connector-specific functions.

\subsection{${\tt haddr\_t} \rightarrow {\tt H5O\_token\_t}$}

Some HDF5 API calls and data structures refer to addresses in the HDF5 using the {\tt haddr\_t} type.
Unfortunately, the concept of an "address" will make no sense for many connectors,
though they may still have some sort of location key (e.g.: a key in a key-value
pair store).

As a part of the VOL work, the HDF5 API was updated to replace the {\tt haddr\_t}
type with a new {\tt H5O\_token\_t} type that represents a more generic object location.
These tokens appear as an opaque byte array of {\tt H5O\_MAX\_TOKEN\_SIZE} bytes that
is only meaningful for a particular VOL connector. They are not intended for
interpretation outside of a VOL connector, though a connector author may provide
an API call to convert their tokens to something meaningful for the storage.

\begin{lstlisting}
typedef struct H5O_token_t {                                                     
    uint8_t __data[H5O_MAX_TOKEN_SIZE];                                          
} H5O_token_t;
\end{lstlisting}

As an example, in the native VOL connector, the token stores an {\tt haddr\_t}
address and addresses can be converted to and from tokens using
{\tt H5VLnative\_addr\_to\_token()} and {\tt H5VLnative\_token\_to\_addr()}.

\begin{lstlisting}
  herr_t H5VLnative_addr_to_token(hid_t loc_id, haddr_t addr, H5O_token_t *token)

  herr_t H5VLnative_token_to_addr(hid_t loc_id, H5O_token_t token, haddr_t *addr)
\end{lstlisting}

Several API calls have also been added to compare tokens and convert tokens to
and from strings.

\begin{lstlisting}
  herr_t H5Otoken_cmp(hid_t loc_id, const H5O_token_t *token1, const H5O_token_t *token2, int *cmp_value)

  herr_t H5Otoken_to_str(hid_t loc_id, const H5O_token_t *token, char **token_str)

  herr_t H5Otoken_from_str(hid_t loc_id, const char *token_str, H5O_token_t *token)
\end{lstlisting}

\subsection{Specific API Call Substitutions}

\subsubsection{${\tt H5Fis\_hdf5()} \rightarrow {\tt H5Fis\_accessible()}$}

@@

\begin{lstlisting}
  htri_t H5Fis_accessible(const char *container_name, hid_t fapl_id)
\end{lstlisting}

\subsubsection{${\tt H5Oget\_info[1|2]()} \rightarrow {\tt H5Oget\_info3()}$ and ${\tt H5Oget\_native\_info()}$}

The {\tt H5Oget\_info1()} and {\tt H5Oget\_info2()} family of HDF5 API calls are often
used by user code to obtain information about an object in the file, however these
calls returned a struct which contained native information and are thus unsuitable
for use with arbitrary VOL connectors.

A new {\tt H5Oget\_info3()} family of API calls has been added to the library which only
return data model information via a new {\tt H5O\_info2\_t} struct. This
struct also returns {\tt H5O\_token\_t} tokens in place of {\tt haddr\_t}
addresses.

\begin{lstlisting}
  H5Oget_info3(hid_t loc_id, H5O_info2_t *oinfo, unsigned fields)

  herr_t H5Oget_info_by_name3(hid_t loc_id, const char *name, H5O_info2_t *oinfo, unsigned fields, hid_t lapl_id)

  herr_t H5Oget_info_by_idx3(hid_t loc_id, const char *group_name, H5_index_t idx_type, H5_iter_order_t order, hsize_t n, H5O_info2_t *oinfo, unsigned fields, hid_t lapl_id)
\end{lstlisting}

\begin{lstlisting}
typedef struct H5O_info2_t {
    unsigned long   fileno;     /* File number that object is located in */
    H5O_token_t     token;      /* Token representing the object        */
    H5O_type_t      type;       /* Basic object type (group, dataset, etc.) */
    unsigned        rc;         /* Reference count of object            */
    time_t          atime;      /* Access time                          */
    time_t          mtime;      /* Modification time                    */
    time_t          ctime;      /* Change time                          */
    time_t          btime;      /* Birth time                           */
    hsize_t         num_attrs;  /* # of attributes attached to object   */
} H5O_info2_t;
\end{lstlisting}

To return the native file format information, {\tt H5Oget\_native\_info()} calls
have been added which can return such data separate from the data model data.

\begin{lstlisting}
  herr_t H5Oget_native_info(hid_t loc_id, H5O_native_info_t *oinfo, unsigned fields)

  herr_t H5Oget_native_info_by_name(hid_t loc_id, const char *name, H5O_native_info_t *oinfo, unsigned fields, hid_t lapl_id)

  herr_t H5Oget_native_info_by_idx(hid_t loc_id, const char *group_name, H5_index_t idx_type, H5_iter_order_t order, hsize_t n, H5O_native_info_t *oinfo, unsigned fields, hid_t lapl_id)
\end{lstlisting}

\begin{lstlisting}
typedef struct H5O_native_info_t {                                               
    H5O_hdr_info_t      hdr;            /* Object header information */          
    /* Extra metadata storage for obj & attributes */                            
    struct {                                                                     
        H5_ih_info_t   obj;             /* v1/v2 B-tree & local/fractal heap for groups, B-tree for chunked datasets */
        H5_ih_info_t   attr;            /* v2 B-tree & heap for attributes */    
    } meta_size;                                                                 
} H5O_native_info_t;
\end{lstlisting}

\subsubsection{${\tt H5Ovisit[1|2]()} \rightarrow {\tt H5Ovisit3()}$}

The callback used in the {\tt H5Ovisit()} family of API calls took an {\tt H5O\_info\_t}
struct parameter. As in {\tt H5Oget\_info()}, this both commingled data model and
native file format information and also used native HDF5 file addresses.

New {\tt H5Ovisit3()} API calls have been created which use the token-based,
data-model-only {\tt H5O\_info\_t} struct in the callback.

\begin{lstlisting}
  herr_t H5Ovisit3(hid_t obj_id, H5_index_t idx_type, H5_iter_order_t order, H5O_iterate2_t op, void *op_data, unsigned fields)

  herr_t H5Ovisit_by_name3(hid_t loc_id, const char *obj_name, H5_index_t idx_type, H5_iter_order_t order, H5O_iterate2_t op, void *op_data, unsigned fields, hid_t lapl_id)
\end{lstlisting}

\begin{lstlisting}
typedef herr_t (*H5O_iterate2_t)(hid_t obj, const char *name, const H5O_info2_t *info, void *op_data)
\end{lstlisting}

\subsubsection{${\tt H5Lget\_info()} \rightarrow {\tt H5Lget\_info2()}$}

The {\tt H5Lget\_info()} API calls were updated to use tokens instead
of addresses in the {\tt H5L\_info\_t} struct.

\begin{lstlisting}
  herr_t H5Lget_info2(hid_t loc_id, const char *name, H5L_info2_t *linfo /*out*/, hid_t lapl_id)

  herr_t H5Lget_info_by_idx2(hid_t loc_id, const char *group_name, H5_index_t idx_type, H5_iter_order_t order, hsize_t n, H5L_info2_t *linfo /*out*/, hid_t lapl_id)
\end{lstlisting}

\begin{lstlisting}
typedef struct {                                                                 
    H5L_type_t          type;           /* Type of link                   */     
    hbool_t             corder_valid;   /* Indicate if creation order is valid */
    int64_t             corder;         /* Creation order                 */     
    H5T_cset_t          cset;           /* Character set of link name     */     
    union {                                                                      
        H5O_token_t     token;          /* Token of location that hard link points to */
        size_t          val_size;       /* Size of a soft link or UD link value */
    } u;                                                                         
} H5L_info2_t;
\end{lstlisting}

\subsubsection{${\tt H5Literate()}$ and ${\tt H5Lvisit()}\rightarrow {\tt H5Literte2()}$ and ${\tt H5Lvisit2()}$}

The callback used in these API calls used the old {\tt H5L\_info\_t} struct, which
used addresses instead of tokens. These callbacks were versioned in the C library
and now take modified {\tt H5L\_iterate2\_t} callbacks which use the new token-based
info structs.

\begin{lstlisting}
  herr_t H5Literate2(hid_t grp_id, H5_index_t idx_type, H5_iter_order_t order, hsize_t *idx, H5L_iterate2_t op, void *op_data)

  herr_t H5Literate_by_name2(hid_t loc_id, const char *group_name, H5_index_t idx_type, H5_iter_order_t order, hsize_t *idx, H5L_iterate2_t op, void *op_data, hid_t lapl_id)

  herr_t H5Lvisit2(hid_t grp_id, H5_index_t idx_type, H5_iter_order_t order, H5L_iterate2_t op, void *op_data)

  herr_t H5Lvisit_by_name2(hid_t loc_id, const char *group_name, H5_index_t idx_type, H5_iter_order_t order, H5L_iterate2_t op, void *op_data, hid_t lapl_id)
\end{lstlisting}

\begin{lstlisting}
typedef herr_t (*H5L_iterate2_t)(hid_t group, const char *name, const H5L_info2_t *info, void *op_data); 
\end{lstlisting}

\subsubsection{${\tt H5Oopen\_by\_addr()} \rightarrow {\tt H5Oopen\_by\_token()}$}

The new {\tt H5Oopen\_by\_token()} API call can be used to open objects by the tokens that are returned by the various "get info", et al. API calls.

\begin{lstlisting}
  hid_t H5Oopen_by_token(hid_t loc_id, H5O_token_t token)
\end{lstlisting}

@@

\section{Language Wrappers}

Due to the parameter type and callback changes that were required in the C
library API regarding the update from {\tt haddr\_t} addresses to
{\tt H5O\_object\_t} tokens and the difficulty in versioning the wrapper
APIs, it was decided to update all of the wrappers to use tokens instead
of addresses. This will allow the language wrappers to make use of the VOL,
but at the expense of backward compatibility.

Information on the C API changes can be found above.

Affected API calls, by language:

\subsection{C++}

\begin{itemize}
    \item The {\tt visit\_operator\_t} callback now uses a {\tt H5O\_info2\_t} parameter instead of {\tt H5O\_info(1)\_t} so the callback can be passed to {\tt H5Ovisit3()} internally. This affects the H5Object::visit() method.
    \item The {\tt H5Location::getObjinfo()} methods now take {\tt H5O\_info2\_t} parameters.
    \item The {\tt H5Location::getLinkInfo()} methods now return {\tt H5L\_info2\_t} structs.
    \item {\tt H5File::isHdf5} uses {\tt H5Fis\_accessible()}, though it always passes H5P\_DEFAULT as the fapl. It will only work with arbitrary VOL connectors if the default VOL connector is changed via the environment variable.
\end{itemize}

The C++ wrappers to not allow opening HDF5 file objects by address or token.

The public H5VL API calls found in {\tt H5VLpublic.h} were NOT added to
the C++ API.

\subsection{Fortran}

As in the C API, these API calls had their structs updated to the token version so
the {\tt h5o\_info\_t}, etc. structs no longer contain native file format information
and the callbacks will need to match the non-deprecated, token-enabled versions.

\begin{itemize}
    \item h5lget\_info\_f
    \item h5lget\_info\_by\_idx\_f
    \item h5literate\_f
    \item h5literate\_by\_name\_f
    \item h5oget\_info\_f
    \item h5oget\_info\_by\_idx\_f
    \item h5oget\_info\_by\_name\_f
    \item h5oopen\_by\_token\_f
    \item h5ovisit\_f
    \item h5ovisit\_by\_name\_f
\end{itemize}

Additionally, {\tt h5fis\_hdf5\_f} was updated to use {\tt H5Fis\_accessible}
internally, though with the same caveat as the C++ implentation: the default
fapl is alwys passed in so arbitrary VOL connectors will only work if the
default VOL connector is changed via the environment variable.

The public H5VL API calls found in {\tt H5VLpublic.h} were also added to
the Fortran wrappers.

\subsection{Java/JNI}

\begin{itemize}
    \item {\tt H5Fis\_hdf5} Will fail when the library is built without deprecated symbols.
    \item {\tt H5Fis\_accessible} is available and takes a fapl, allowing it to work with arbitrary VOL connectors.
    \item The {\tt H5(O|L)get\_info}, {\tt H5(O|L)visit}, and {\tt H5Literate} calls were updated as in the C library.
    \item {\tt H5Oget\_native\_info\_by\_name} et al. were added and they work as in the C library (e.g.: essentially native VOL connector only).
    \item {\tt H5Oopen\_by\_addr} was replaced with {\tt H5Oopen\_by\_token}.
    \item The public API calls in {\tt H5VLpublic.h} were added to the JNI.
\end{itemize}

@@

\section{Compatibility}

@@

\begin{longtable}{ |>{\raggedright\arraybackslash}p{\linewidth}| }
    \hline
    H5Aget\_num\_attrs (deprecated) \\
    H5Aiterate1 (deprecated) \\
    \hline
    H5Ddebug \\
    H5Dformat\_convert \\
    H5Dget\_chunk\_index\_type \\
    H5Dget\_chunk\_info \\
    H5Dget\_chunk\_info\_by\_coord \\
    H5Dget\_chunk\_storage\_size \\
    H5Dget\_num\_chunks \\
    H5Dread\_chunk H5Dwrite\_chunk \\
    \hline
    H5FD* \\
    \hline
    H5Fclear\_elink\_file\_cache \\
    H5Fformat\_convert \\
    H5Fget\_dset\_no\_attrs\_hint \\
    H5Fget\_eoa H5Fget\_file\_image \\
    H5Fget\_filesize \\
    H5Fget\_free\_sections \\
    H5Fget\_freespace \\
    H5Fget\_info1 (deprecated) \\
    H5Fget\_info2 \\
    H5Fget\_mdc\_config \\
    H5Fget\_mdc\_hit\_rate \\
    H5Fget\_mdc\_image\_info \\
    H5Fget\_mdc\_logging\_status \\
    H5Fget\_mdc\_size \\
    H5Fget\_metadata\_read\_retry\_info \\
    H5Fget\_mpi\_atomicity \\
    H5Fget\_page\_buffering\_stats \\
    H5Fget\_vfd\_handle \\
    H5Fincrement\_filesize \\
    H5Fis\_hdf5 (deprecated) \\
    H5Freset\_mdc\_hit\_rate\_stats \\
    H5Freset\_page\_buffering\_stats \\
    H5Fset\_dset\_no\_attrs\_hint \\
    H5Fset\_latest\_format (deprecated) \\
    H5Fset\_libver\_bounds \\
    H5Fset\_mdc\_config \\
    H5Fset\_mpi\_atomicity \\
    H5Fstart\_mdc\_logging \\
    H5Fstart\_swmr\_write \\
    H5Fstop\_mdc\_logging \\
    \hline
    H5Gget\_comment (deprecated) \\
    H5Giterate (deprecated) \\
    H5Gget\_info \\
    H5Gget\_info\_by\_name \\
    H5Gget\_info\_by\_idx \\
    H5Gget\_objinfo (deprecated) \\
    H5Gget\_objname\_by\_idx (deprecated) \\
    H5Gget\_objtype\_by\_idx (deprecated) \\
    H5Gset\_comment (deprecated) \\
    \hline
    H5Lget\_info1 (deprecated) \\
    H5Lget\_info\_by\_idx1 (deprecated) \\
    H5Literate1 (deprecated) \\
    H5Literate\_by\_name1 (deprecated) \\
    H5Lvisit1 (deprecated) \\
    H5Lvisit\_by\_name1 (deprecated) \\
    \hline
    H5Oare\_mdc\_flushes\_disabled \\
    H5Odisable\_mdc\_flushes \\
    H5Oenable\_mdc\_flushes \\
    H5Oget\_comment \\
    H5Oget\_comment\_by\_name \\
    H5Oget\_info\_by\_idx1 (deprecated) \\
    H5Oget\_info\_by\_idx2 (deprecated)\\
    H5Oget\_info\_by\_name1 (deprecated) \\
    H5Oget\_info\_by\_name2 (deprecated)\\
    H5Oget\_info1 (deprecated) \\
    H5Oget\_info2 (deprecated) \\
    H5Oopen\_by\_addr (deprecated) \\
    H5Oset\_comment \\
    H5Oset\_comment\_by\_name \\
    H5Ovisit1 (deprecated) \\
    H5Ovisit\_by\_name1 (deprecated) \\
    H5Ovisit2 (deprecated) \\
    H5Ovisit\_by\_name2 (deprecated) \\
    \hline
\caption{Alphabetical list of HDF5 API calls specific to the native VOL connector}
\end{longtable}
